Precise spiking motifs in neurobiological and neuromorphic data

### 2022-11-14 manuscript.tex
Section 5

Artificial intelligence has made huge advances in the past decades, now deep learning algorithms outperform humans at complex tasks like natural image recognition or abstract strategy board games. Machine learning algorithms still suffer from adversarial attacks or a lack of generalization capacity but their main weakness, compared to biological neural networks, rely on their poor energy efficiency. Neuromorphic engineering intends to mimic the neural bases of communication with a wide variety of technics, from strictly analog circuits to software-based neuromorphic systems, and to develop tools improving the capacities of current artificial intelligence~\citep{roy_towards_2019}. Because the reduced energy consumption of biological networks can be explained by the use of spikes and asynchronous responses to exchange information (ref), neuromorphic chips use this parallel and event-based representation to make energy efficient computations. This is also the case for Dynamic Vision Sensors (DVS) which provide a stream of binary asynchronous events signaling detectable changes in luminance. These devices, also named ``silicon retinas'' (see Figure \ref{fig:silicon_retina}), show great improvements in terms of memory allocation, or power consumption, for the recording of a visual scene. Another important distinction with classical von Neumann architectures is the localized memory of this new type of chips. It can be materialized by the capacity of the physical connections between the processing units to store information~\citep{markovic_physics_2020}. An example of such connection, directly inspired by synaptic plasticity, is the memristor~\citep{rasetto_challenges_2022} for which the resistance value can be dynamically adjusted. Using these event-based computations as a building brick, neuromorphic engineering proposes new hardware designs perfect to simulate SNNs and use the full power of asynchronous computations observed in biological systems. This field of research is inspired by neuroscientific advances and a computational formalism to design innovative architectures and, by reproducing such mechanisms, it is interesting to study neural circuitry. Many connections can be drawn between neuromorphic engineering and computational neuroscience to aim at solving both research and technology challenges~\citep{zenke_visualizing_2021}. Just as communication between neurons can be illustrated by a raster plot, information exchanges in neuromorphic hardware are described as event streams by an Address-Event Representation (AER). We will use indifferently \textit{events} or \textit{spikes} to describe the same binary and discrete processes and, in this section, we will extend the review of the use of precise spike timing to this emerging field. There exist different types of event-based sensing devices for sound~\citep{chan_aer_2007} and touch~\citep{haessig_event-based_2020} but first we focus only on neuromorphic cameras to review different methods using efficiently the dynamics of event streams. Then, we dedicate one subsection to the implementation of delay-based algorithms on neuromorphic chips.  

>>>>

Artificial intelligence has made huge advances in the past decades and deep learning algorithms nowadays outperform humans at complex tasks like natural image recognition or abstract strategy board games. Yet, machine learning algorithms suffer from adversarial attacks or a lack of generalization capacity but their main weakness, compared to biological neural networks, rely on their poor energy efficiency. Neuromorphic engineering intends to mimic the neural bases of communication with a wide variety of technics, from strictly analog circuits to software-based neuromorphic systems, and to develop tools improving the capacities of current artificial intelligence~\citep{roy_towards_2019}. Because the reduced energy consumption of biological networks can be explained by the use of spikes and asynchronous responses to exchange information (ref), neuromorphic chips use this parallel and event-based representation to make energy efficient computations. This is also the case for Dynamic Vision Sensors (DVS) which provide a stream of binary asynchronous events signaling detectable changes in luminance. These devices, also named ``silicon retinas'' (see Figure \ref{fig:silicon_retina}), show great improvements in terms of memory allocation, or power consumption, for the recording of a visual scene. Another important distinction with classical von Neumann architectures is the localized memory of this new type of chips. It can be materialized by the capacity of the physical connections between the processing units to store information~\citep{markovic_physics_2020}. An example of such connection, directly inspired by synaptic plasticity, is the memristor~\citep{rasetto_challenges_2022} for which the resistance value can be dynamically adjusted. Using these event-based computations as a building brick, neuromorphic engineering proposes new hardware designs perfect to simulate SNNs and use the full power of asynchronous computations observed in biological systems. This field of research is inspired by neuroscientific advances and a computational formalism to design innovative architectures and, by reproducing such mechanisms, it is interesting to study neural circuitry. Many connections can be drawn between neuromorphic engineering and computational neuroscience to aim at solving both research and technology challenges~\citep{zenke_visualizing_2021}. Just as communication between neurons can be illustrated by a raster plot, information exchanges in neuromorphic hardware are described as event streams by an Address-Event Representation (AER). We will use indifferently \textit{events} or \textit{spikes} to describe the same binary and discrete processes and, in this section, we will extend the review of the use of precise spike timing to this emerging field. There exist different types of event-based sensing devices for sound~\citep{chan_aer_2007} and touch~\citep{haessig_event-based_2020} but first we focus only on neuromorphic cameras to review different methods using efficiently the dynamics of event streams. Then, we dedicate one subsection to the implementation of delay-based algorithms on neuromorphic chips.  
